Numerical experiment investigating the influence of drag on trajectory patterns of floating macroalgae

### 2021-03-23 thesis_chapter_3.Rmd
chapter 3 updates

heatmap_RK4 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_RK4, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = p_RK4, bins = 80, aes(x = lon, y = lat), legend = FALSE) +  
  scale_fill_continuous(type = "gradient", limits = c(1, 1000)) +
  geom_path(data = p_RK4_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("") +
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

heatmap_Min_Kfloat_H100_W00 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_EE, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Min_Kfloat_H100_W00, bins = 80, aes(x = lon, y = lat)) +  
  scale_fill_continuous(type = "gradient",limits = c(1, 1000)) +
  geom_path(data = Min_Kfloat_H100_W00_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  #ggtitle("H100W100") +
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

heatmap_Min_Kfloat_H095_W05 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_EE, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Min_Kfloat_H095_W05, bins = 80, aes(x = lon, y = lat)) +  
  scale_fill_continuous(type = "gradient",limits = c(1, 1000)) +
  geom_path(data = Min_Kfloat_H095_W05_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  #ggtitle("H095W05") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

heatmap_Min_Kfloat_H090_W10 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_EE, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Min_Kfloat_H090_W10, bins = 80, aes(x = lon, y = lat)) +  
  scale_fill_continuous(type = "gradient",limits = c(1, 1000)) +
  geom_path(data = Min_Kfloat_H090_W10_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  #ggtitle("H090W10") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

heatmap_Min_Kfloat_H085_W15 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_EE, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Min_Kfloat_H085_W15, bins = 80, aes(x = lon, y = lat)) +  
  scale_fill_continuous(type = "gradient", limits = c(1, 1000)) +
  geom_path(data = Min_Kfloat_H085_W15_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  #ggtitle("H085W15") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

heatmap_Mean_Kfloat_H100_W00 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_EE, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Mean_Kfloat_H100_W00, bins = 80, aes(x = lon, y = lat)) +  
  scale_fill_continuous(type = "gradient", limits = c(1, 1000)) +
  geom_path(data = Mean_Kfloat_H100_W00_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

heatmap_Mean_KFloat_H095_W05 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = k_app1, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Mean_KFloat_H095_W05, bins = 80, aes(x = lon, y = lat)) +  scale_fill_continuous(type = "gradient", limits = c(1, 1000)) +
  geom_path(data = Mean_KFloat_H095_W05_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

heatmap_Mean_KFloat_H090_W10 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = k_app2, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Mean_KFloat_H090_W10, bins = 80, aes(x = lon, y = lat)) +
  scale_fill_continuous(type = "gradient", limits = c(1, 1000)) +
  geom_path(data = Mean_KFloat_H090_W10_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

heatmap_Mean_KFloat_H085_W15 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = k_app2, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Mean_KFloat_H085_W15, bins = 80, aes(x = lon, y = lat)) +
  scale_fill_continuous(type = "gradient", limits = c(1, 1000)) +
  geom_path(data = Mean_KFloat_H085_W15_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

heatmap_Max_KFloat_H100_W00 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = k_app2, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Max_Kfloat_H100_W00, bins = 80, aes(x = lon, y = lat)) +
  scale_fill_continuous(type = "gradient", limits = c(1, 1000)) +
  geom_path(data = Max_Kfloat_H100_W00_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

heatmap_Max_KFloat_H095_W05 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = k_app2, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Max_Kfloat_H095_W05, bins = 80, aes(x = lon, y = lat)) +
  scale_fill_continuous(type = "gradient", limits = c(1, 1000)) +
  geom_path(data = Max_Kfloat_H095_W05_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  theme(plot.title = element_text(hjust = 0.5)) + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

heatmap_Max_KFloat_H090_W10 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = k_app2, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Max_Kfloat_H090_W10, bins = 80, aes(x = lon, y = lat)) +
  scale_fill_continuous(type = "gradient", limits = c(1, 1000)) +
  geom_path(data = Max_Kfloat_H090_W10_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

heatmap_Max_KFloat_H085_W15 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = k_app2, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Max_Kfloat_H085_W15, bins = 80, aes(x = lon, y = lat)) +
  scale_fill_continuous(type = "gradient", limits = c(1, 1000)) +
  geom_path(data = Max_Kfloat_H085_W15_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))
```

>>>>

heatmap_RK4 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_RK4, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = p_RK4, bins = 80, aes(x = lon, y = lat), legend = FALSE) +  
  scale_fill_continuous(type = "gradient", limits = c(1, 1100)) +
  geom_path(data = p_RK4_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  ggtitle("") +
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

heatmap_Min_Kfloat_H100_W00 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_EE, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Min_Kfloat_H100_W00, bins = 80, aes(x = lon, y = lat)) +  
  scale_fill_continuous(type = "gradient",limits = c(1, 1100)) +
  geom_path(data = Min_Kfloat_H100_W00_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  #ggtitle("H100W100") +
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

heatmap_Min_Kfloat_H095_W05 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_EE, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Min_Kfloat_H095_W05, bins = 80, aes(x = lon, y = lat)) +  
  scale_fill_continuous(type = "gradient",limits = c(1, 1100)) +
  geom_path(data = Min_Kfloat_H095_W05_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  #ggtitle("H095W05") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

heatmap_Min_Kfloat_H090_W10 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_EE, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Min_Kfloat_H090_W10, bins = 80, aes(x = lon, y = lat)) +  
  scale_fill_continuous(type = "gradient",limits = c(1, 1100)) +
  geom_path(data = Min_Kfloat_H090_W10_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  #ggtitle("H090W10") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

heatmap_Min_Kfloat_H085_W15 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_EE, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Min_Kfloat_H085_W15, bins = 80, aes(x = lon, y = lat)) +  
  scale_fill_continuous(type = "gradient", limits = c(1, 1100)) +
  geom_path(data = Min_Kfloat_H085_W15_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  #ggtitle("H085W15") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

heatmap_Mean_Kfloat_H100_W00 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = p_EE, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Mean_Kfloat_H100_W00, bins = 80, aes(x = lon, y = lat)) +  
  scale_fill_continuous(type = "gradient", limits = c(1, 1100)) +
  geom_path(data = Mean_Kfloat_H100_W00_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

heatmap_Mean_KFloat_H095_W05 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = k_app1, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Mean_KFloat_H095_W05, bins = 80, aes(x = lon, y = lat)) +  scale_fill_continuous(type = "gradient", limits = c(1, 1100)) +
  geom_path(data = Mean_KFloat_H095_W05_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

heatmap_Mean_KFloat_H090_W10 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = k_app2, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Mean_KFloat_H090_W10, bins = 80, aes(x = lon, y = lat)) +
  scale_fill_continuous(type = "gradient", limits = c(1, 1100)) +
  geom_path(data = Mean_KFloat_H090_W10_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

heatmap_Mean_KFloat_H085_W15 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = k_app2, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Mean_KFloat_H085_W15, bins = 80, aes(x = lon, y = lat)) +
  scale_fill_continuous(type = "gradient", limits = c(1, 1100)) +
  geom_path(data = Mean_KFloat_H085_W15_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

heatmap_Max_KFloat_H100_W00 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = k_app2, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Max_Kfloat_H100_W00, bins = 80, aes(x = lon, y = lat)) +
  scale_fill_continuous(type = "gradient", limits = c(1, 1100)) +
  geom_path(data = Max_Kfloat_H100_W00_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

heatmap_Max_KFloat_H095_W05 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = k_app2, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Max_Kfloat_H095_W05, bins = 80, aes(x = lon, y = lat)) +
  scale_fill_continuous(type = "gradient", limits = c(1, 1100)) +
  geom_path(data = Max_Kfloat_H095_W05_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  theme(plot.title = element_text(hjust = 0.5)) + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

heatmap_Max_KFloat_H090_W10 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = k_app2, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Max_Kfloat_H090_W10, bins = 80, aes(x = lon, y = lat)) +
  scale_fill_continuous(type = "gradient", limits = c(1, 1100)) +
  geom_path(data = Max_Kfloat_H090_W10_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))

heatmap_Max_KFloat_H085_W15 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  #geom_bin2d(data = k_app2, bins = 80, aes(x = lon, y = lat)) +
  geom_hex(data = Max_Kfloat_H085_W15, bins = 80, aes(x = lon, y = lat)) +
  scale_fill_continuous(type = "gradient", limits = c(1, 1100)) +
  geom_path(data = Max_Kfloat_H085_W15_mean,aes(x = lon, y = lat, color = 'red'), show.legend = FALSE) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5))
```
